---
title: "Data Upload MD1"
author: "Julie Norman"
date: '2022-06-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(readr)
library(readxl)
library(tidyverse)

library(reshape2)
library(openxlsx)
```


## State Demographic Data
Source: https://corgis-edu.github.io/corgis/csv/state_demographics/

```{r}
dem_df <- read_csv("Data Sets/state_demographics.csv")

dem_df$Expand <- ifelse(dem_df$State == "Wyoming" | dem_df$State ==  "South Dakota" | dem_df$State ==  "Wisconsin" | dem_df$State ==  "Kansas" | dem_df$State ==  "Tennessee" | dem_df$State ==  "Mississippi" | dem_df$State ==  "Alabama" | dem_df$State ==  "Georgia"  | dem_df$State ==  "North Carolina" | dem_df$State ==  "South Carolina" | dem_df$State ==  "Texas", 0, 1 )


dem_df2 <- dem_df %>% 
  filter((Expand == 0 |  State == "Indiana"|   State == "Illinois"|     State == "Louisiana"|    State == "Virginia" | State == "North Dakota"   | State == "Arkansas" | State == "North Dakota" | State == "Minnesota" | State == "Nevada" | State == "Indiana" | State == "Missouri") & State != "Texas")

# State == "Michigan"| State == "Nebraska"| State == "West Virginia" | State == "Iowa"| | State == "Oklahoma"  | State == "Kentucky" | State == "Colorado" |  State == "Ohio"| State == "District of Columbia" | State == "Montana" | State == "Idaho" 


demMd_df <- aggregate(dem_df2, list(dem_df2$Expand), median)

dem_df2$Expand <- as.factor(dem_df2$Expand)

demMn_df <- aggregate(dem_df2, list(dem_df2$Expand), mean)

demSm_df <- dem_df2[, c( 3, 4)] %>% 
  group_by(dem_df2$Expand) %>% 
  summarise(`Population.2014 Population` = sum(`Population.2014 Population`), `Population.2010 Population` = sum(`Population.2010 Population`))

#View(filter(dem_df, dem_df$Expand == 1))

```

#### States of Interest

Years 2011 - 2019

##### Expanded
* Montana
* North Dakota
* Nebraska
* Minnesota
* Iowa
* Louisiana
* Arkansas
* Kentucky
* West Virginia
* Virginia 

##### Not Expanded
* Wyoming
* South Dakota
* Wisconsin
* Kansas
* Tennessee
* Mississippi
* Alabama
* Georgia
* Florida
* North Carolina
* South Carolina

maybe * Texas

##### Expanded
* Montana
* North Dakota
* Nebraska
* Minnesota
* Iowa
* Louisiana
* Arkansas
* Kentucky
* West Virginia
* Virginia 


### Graphics

```{r}
ggplot(dem_df2, aes(x = Expand, y = `Population.2014 Population`, fill = Expand)) +
  geom_boxplot() +
  ggtitle('2014 Population') 

```

```{r}
ggplot(dem_df2, aes(x = Expand, y = `Income.Per Capita Income`, fill = Expand)) +
  geom_boxplot() +
  ggtitle('Income Per Capita') 


```
```{r}


ggplot(dem_df2, aes(x = Expand, y = dem_df2$`Ethnicities.White Alone`, fill = Expand)) +
  geom_boxplot() +
  ggtitle("Ethnicities.white Alone") 


```

## Health Data

### Alabama


#### 2011

```{r}
#read files
al11_df2 <- read_excel("Data Sets/Alabama Data/2011 County Health Ranking Alabama Data - v4.xls", 
    sheet = 2)
al11_df2  <- rename(al11_df2, "1" = "...1", "2" = "...2", "3" = "...3", "Outcomes" = "...5", "Rank" = "...7" )

al11_df3 <- read_excel("Data Sets/Alabama Data/2011 County Health Ranking Alabama Data - v4.xls", 
    sheet = 3)
al11_df3  <- rename(al11_df3, "1" = "...1", "2" = "...2", "3" = "...3", "Mortal" = "...5", "Morbid" = "...7", "Health.Behaviors" = "...9", "Clinical.Care" = "...11", "SocEcon.Factors" = "...13", "Physical.Envir" = "...15")

al11_df4 <- read_excel("Data Sets/Alabama Data/2011 County Health Ranking Alabama Data - v4.xls", 
    sheet = 4)
al11_df4  <- rename(al11_df4, "1" = "...1", "2" = "...2", "3" = "...3", "Mortal" = "...5", "6" = "...6", "Morbid" = "...7", "8" = "...8", "Health.Behaviors" = "...9", "Clinical.Care" = "...11", "SocEcon.Factors" = "...13", "Physical.Envir" = "...15") #incomplete

al11_df5 <- read_excel("Data Sets/Alabama Data/2011 County Health Ranking Alabama Data - v4.xls", 
    sheet = 5)

# put all data frames into list
al11df_list <- list(al11_df2, al11_df3, al11_df4, al11_df5)

# merge all data frames in list
al11D_df <- al11df_list %>% reduce(full_join, by = '...1')

# add row 1 to column name, delete row
names(al11D_df) <- paste(names(al11D_df), al11D_df[1, ], sep = "_")
al11D_df <- al11D_df[-1,]

# Delete Duplicate Columns
al11_df <- al11D_df[!duplicated(as.list(al11D_df))]



```

```{r}
al11_dfA <- read.xlsx("Data Sets/Alabama Data/2011 County Health Ranking Alabama Data - v4.xlsx", 
    sheet = 2,
    fillMergedCells = TRUE, colNames = FALSE)


al11_dfB <- read.xlsx("Data Sets/Alabama Data/2011 County Health Ranking Alabama Data - v4.xlsx", 
    sheet = 3,
    fillMergedCells = TRUE, colNames = FALSE)


al11_dfC <- read.xlsx("Data Sets/Alabama Data/2011 County Health Ranking Alabama Data - v4.xlsx", 
    sheet = 4,
    fillMergedCells = TRUE, colNames = FALSE)


al11_dfE <- read.xlsx("Data Sets/Alabama Data/2011 County Health Ranking Alabama Data - v4.xlsx", 
    sheet = 5,
    fillMergedCells = TRUE, colNames = FALSE)

# put all data frames into list
al11df_list <- list(al11_dfA, al11_dfB, al11_dfC, al11_dfD)

# merge all data frames in list
al11D_df <- al11df_list %>% reduce(full_join, by = 'X1')

# remove extra row, unsure how it appeared
al11D_df <- al11D_df[-2,]

# Delete Duplicate Columns
al11D_df <- al11D_df[!duplicated(as.list(al11D_df))]

# fill first row NA with blanks
al11D_df2 <- al11D_df[1,]
 al11D_df2[is.na(al11D_df2)] <- ""
al11D_df[1,] <- al11D_df2[1,]
 
# merge first two rows for new column names
colnames(al11D_df) <- paste(sep = '.', as.character(unlist(al11D_df[1,])), as.character(unlist(al11D_df[2,])))
al11_df <- al11D_df[-c(1,2), ]

# Add Year
al11_df$.Year <- 2011

head(al11_df$.Year)
```

```{r}
#clean
df = rename(df, new_col01 = old_col01, new_col02 = old_col02, ...)
```


## TEST

```{r}
testdf<- X2011_County_Health_Ranking_Alabama_Data_v4 <- read.xlsx("Data Sets/Alabama Data/2011 County Health Ranking Alabama Data - v4.xlsx", 
    sheet = "Outcomes & Factors Rankings",
    fillMergedCells = TRUE, colNames = FALSE) 

df <- testdf[1,]
 df[is.na(df)] <- ""
testdf[1,] <- df[1,]
 
colnames(testdf) <- paste(sep = '.', as.character(unlist(testdf[1,])), as.character(unlist(testdf[2,])))
testdf <- testdf[-c(1,2), ]


```

```{r}
d <- X2011_County_Health_Ranking_Alabama_Data_v4 <- read_excel("Data Sets/Alabama Data/2011 County Health Ranking Alabama Data - v4.xls", 
    sheet = "Outcomes & Factors Rankings")
header <- colnames(d)
header <- header[!grepl("...", header)]

name_cols <- d[1,]
d <- d[-c(1,2),]
colnames(d) <- name_cols

header <- factor(rep(header, each = nrow(d) * (length(unique(colnames(d)))-1)),
                 levels = header)
header
```



library(readxl)
library(reshape)

# load an example excel file and see how it looks
d <- as.data.frame(read_excel("~/Bureau/Merged_Headers_Example.xls"))
d

##     X__1 January X__2 X__3 February X__4 X__5 March X__6 X__7
## 1 SECTOR    var1 var2 var3     var1 var2 var3  var1 var2 var3
## 2   AAAA       2    8    2        0    0    5     2    3    9
## 3   BBBB       9    3    8        4    2    6     8    6    8
## 4   CCCC       6    0   10        7    4    9     5    8    2
## 5   DDDD       0    1    2        2    5    7     4    3    2
## 6   EEEE       4    8    1        8   10    8     5   10    4
## 7   FFFF       1    0   10        2    1    4     1    3    3


# Capture the values of the merged cells on the first line
header <- colnames(d)
header <- header[!grepl("X__", header)]

# remove the first line and set the colomn names as the second line
name_cols <- d[1,]
d <- d[-1,]
colnames(d) <- name_cols

# Repeat the months the correct number of time 
# to be adapted depending on the structure of the file
# e.g. `-1` here is to not count the first column
header <- factor(rep(header, each = nrow(d) * (length(unique(colnames(d)))-1)),
                 levels = header)

```{r}

```

