---
title: "Data Upload MD1"
author: "Julie Norman"
date: '2022-06-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(readr)
library(readxl)
library(tidyverse)
library(openxlsx)

#library(reshape2)
#library(data.table)
```


#### States of Interest

Years 2011 - 2019

##### Expanded and Using
* Arkansas
* Florida
* Iowa
* Kentucky
* Louisiana
* Minnesota
* Montana
* North Dakota
* Nebraska
* West Virginia
* Virginia 

##### Not Expanded
* Alabama
* Florida
* Georgia
* Kansas

* Mississippi
* North Carolina Need
* South Dakota
* South Carolina 

* Tennessee
* Wisconsin
* Wyoming





maybe * Texas
maybe remove: tennessee, south dakota, Georgia, Kansas  



#### Data not to compare over time
* Primary Care Physicians
* Dentists
* Dentists Previous Data
* High School Graduation
* Limited Access to Healthy Foods


## Not Expanded States Data 

```{r}
# read csv
al_df <- read_csv("Data Sets/Alabama_all.csv")
fl_df <- read_csv("Data Sets/Florida_all.csv")
ks_df <- read_csv("Data Sets/Kansas_all.csv")
ms_df <- read_csv("Data Sets/Mississippi_all.csv")
sc_df <- read_csv("Data Sets/South Carolina_all.csv")
tn_df <- read_csv("Data Sets/Tennessee_all.csv")
wi_df <- read_csv("Data Sets/Wisconsin_all.csv")
wy_df <- read_csv("Data Sets/Wyoming_all.csv")

```






## MISC TEST

```{r}
testdf<- X2011_County_Health_Ranking_Alabama_Data_v4 <- read.xlsx("Data Sets/Alabama Data/2011 County Health Ranking Alabama Data - v4.xlsx", 
    sheet = "Outcomes & Factors Rankings",
    fillMergedCells = TRUE, colNames = FALSE) 

df <- testdf[1,]
 df[is.na(df)] <- ""
testdf[1,] <- df[1,]
 
colnames(testdf) <- paste(sep = '.', as.character(unlist(testdf[1,])), as.character(unlist(testdf[2,])))
testdf <- testdf[-c(1,2), ]


```

```{r}
d <- X2011_County_Health_Ranking_Alabama_Data_v4 <- read_excel("Data Sets/Alabama Data/2011 County Health Ranking Alabama Data - v4.xls", 
    sheet = "Outcomes & Factors Rankings")
header <- colnames(d)
header <- header[!grepl("...", header)]

name_cols <- d[1,]
d <- d[-c(1,2),]
colnames(d) <- name_cols

header <- factor(rep(header, each = nrow(d) * (length(unique(colnames(d)))-1)),
                 levels = header)
header
```

```{r}
# # fill first row NA with blanks
# ga19D_df2 <- ga19D_df[1,]
#  ga19D_df2[is.na(ga19D_df2)] <- ""
# ga19D_df[1,] <- ga19D_df2[1,]
```



library(readxl)
library(reshape)

# load an example excel file and see how it looks
d <- as.data.frame(read_excel("~/Bureau/Merged_Headers_Example.xls"))
d

##     X__1 January X__2 X__3 February X__4 X__5 March X__6 X__7
## 1 SECTOR    var1 var2 var3     var1 var2 var3  var1 var2 var3
## 2   AAAA       2    8    2        0    0    5     2    3    9
## 3   BBBB       9    3    8        4    2    6     8    6    8
## 4   CCCC       6    0   10        7    4    9     5    8    2
## 5   DDDD       0    1    2        2    5    7     4    3    2
## 6   EEEE       4    8    1        8   10    8     5   10    4
## 7   FFFF       1    0   10        2    1    4     1    3    3


# Capture the values of the merged cells on the first line
header <- colnames(d)
header <- header[!grepl("X__", header)]

# remove the first line and set the colomn names as the second line
name_cols <- d[1,]
d <- d[-1,]
colnames(d) <- name_cols

# Repeat the months the correct number of time 
# to be adapted depending on the structure of the file
# e.g. `-1` here is to not count the first column
header <- factor(rep(header, each = nrow(d) * (length(unique(colnames(d)))-1)),
                 levels = header)

```{r}
al11_dfA <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2011 County Health Ranking Alabama Data - v4.xlsx", 
    sheet = 2,
    fillMergedCells = TRUE, colNames = FALSE) %>%
  rename_with(.fn = \(cn) sapply(.[1.2,], \(c) paste(na.omit(c), collapse = "_"))) %>%
  slice(3:n())
```

```{r}
# count na 
na_count <-sapply(wy_df2, function(y) sum(is.na(y)))
na_count
```

