---
title: "Data Upload MD1"
author: "Julie Norman"
date: '2022-06-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(readr)
library(readxl)
library(tidyverse)
library(openxlsx)

library(reshape2)
library(data.table)
```




#### States of Interest

Years 2011 - 2019

##### Expanded
* Montana
* North Dakota
* Nebraska
* Minnesota
* Iowa
* Louisiana
* Arkansas
* Kentucky
* West Virginia
* Virginia 

##### Not Expanded
* Wyoming
* South Dakota
* Wisconsin
* Kansas
* Tennessee
* Mississippi
* Alabama
* Georgia
* Florida
* North Carolina
* South Carolina

maybe * Texas

##### Expanded
* Montana
* North Dakota
* Nebraska
* Minnesota
* Iowa
* Louisiana
* Arkansas
* Kentucky
* West Virginia
* Virginia 




## Health Data

### Alabama


#### 2011

```{r}
# read data
al11_dfA <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2011 County Health Ranking Alabama Data - v4.xlsx", 
    sheet = 2,
    fillMergedCells = TRUE, colNames = FALSE)

al11_dfB <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2011 County Health Ranking Alabama Data - v4.xlsx", 
    sheet = 3,
    fillMergedCells = TRUE, colNames = FALSE)

al11_dfC <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2011 County Health Ranking Alabama Data - v4.xlsx", 
    sheet = 4,
    fillMergedCells = TRUE, colNames = FALSE)

al11_dfD <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2011 County Health Ranking Alabama Data - v4.xlsx", 
    sheet = 5,
    fillMergedCells = TRUE, colNames = FALSE)

# put all data frames into list
al11df_list <- list(al11_dfA, al11_dfB, al11_dfC, al11_dfD)

# merge all data frames in list
al11D_df <- al11df_list %>% reduce(full_join, by = 'X1')

# Delete Duplicate Columns and row (unsure where row came from)
al11D_df <- al11D_df[-2, !duplicated(as.list(al11D_df))]

# # fill first row NA with blanks
# al11D_df2 <- al11D_df[1,]
#  al11D_df2[is.na(al11D_df2)] <- ""
# al11D_df[1,] <- al11D_df2[1,]
 
# merge first two rows for new column names
colnames(al11D_df) <- paste(sep = '.', as.character(unlist(al11D_df[1,])), as.character(unlist(al11D_df[2,])))
al11_df <- al11D_df[-c(1,2), ]

# Add Year
al11_df$Year <- 2011


```

#### 2012

```{r}
# read data
al12_dfA <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2012 County Health Ranking Alabama Data - v4.xlsx", 
    sheet = 2,
    fillMergedCells = TRUE, colNames = FALSE)

al12_dfB <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2012 County Health Ranking Alabama Data - v4.xlsx", 
    sheet = 3,
    fillMergedCells = TRUE, colNames = FALSE)

al12_dfC <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2012 County Health Ranking Alabama Data - v4.xlsx", 
    sheet = 4,
    fillMergedCells = TRUE, colNames = FALSE)

al12_dfD <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2012 County Health Ranking Alabama Data - v4.xlsx", 
    sheet = 5,
    fillMergedCells = TRUE, colNames = FALSE)

# put all data frames into list
al12df_list <- list(al12_dfA, al12_dfB, al12_dfC, al12_dfD)

# merge all data frames in list
al12D_df <- al12df_list %>% reduce(full_join, by = 'X1')

# Delete Duplicate Columns and row (unsure where row came from)
al12D_df <- al12D_df[-2, !duplicated(as.list(al12D_df))]
# 
# # fill first row NA with blanks
# al12D_df2 <- al12D_df[1,]
#  al12D_df2[is.na(al12D_df2)] <- ""
# al12D_df[1,] <- al12D_df2[1,]
 
# merge first two rows for new column names
colnames(al12D_df) <- paste(sep = '.', as.character(unlist(al12D_df[1,])), as.character(unlist(al12D_df[2,])))
al12_df <- al12D_df[-c(1,2), ]

# Add Year
al12_df$Year <- 2012


```

#### 2013 

```{r}
# read data
al13_dfA <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2013 County Health Ranking Alabama Data - v1_1.xlsx", 
    sheet = 2,
    fillMergedCells = TRUE, colNames = FALSE)

al13_dfB <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2013 County Health Ranking Alabama Data - v1_1.xlsx", 
    sheet = 3,
    fillMergedCells = TRUE, colNames = FALSE)

al13_dfC <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2013 County Health Ranking Alabama Data - v1_1.xlsx", 
    sheet = 4,
    fillMergedCells = TRUE, colNames = FALSE)

al13_dfD <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2013 County Health Ranking Alabama Data - v1_1.xlsx", 
    sheet = 5,
    fillMergedCells = TRUE, colNames = FALSE)

al13_dfE <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2013 County Health Ranking Alabama Data - v1_1.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

# put all data frames into list
al13df_list <- list(al13_dfA, al13_dfB, al13_dfC, al13_dfD, al13_dfE)

# merge all data frames in list
al13D_df <- al13df_list %>% reduce(full_join, by = 'X1')

# Delete Duplicate Columns 
al13D_df <- al13D_df[!duplicated(as.list(al13D_df))]

# fill first row NA with blanks
al13D_df2 <- al13D_df[1,]
 al13D_df2[is.na(al13D_df2)] <- ""
al13D_df[1,] <- al13D_df2[1,]
 
# # merge first two rows for new column names
# colnames(al13D_df) <- paste(sep = '.', as.character(unlist(al13D_df[1,])), as.character(unlist(al13D_df[2,])))
# al13_df <- al13D_df[-c(1,2), ]

# Add Year
al13_df$Year <- 2013


```

#### 2014

```{r}
# read data
al14_dfA <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2014 County Health Rankings Alabama Data - v6.xlsx", 
    sheet = 2,
    fillMergedCells = TRUE, colNames = FALSE)

al14_dfB <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2014 County Health Rankings Alabama Data - v6.xlsx", 
    sheet = 3,
    fillMergedCells = TRUE, colNames = FALSE)

al14_dfC <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2014 County Health Rankings Alabama Data - v6.xlsx", 
    sheet = 4,
    fillMergedCells = TRUE, colNames = FALSE)

al14_dfD <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2014 County Health Rankings Alabama Data - v6.xlsx", 
    sheet = 5,
    fillMergedCells = TRUE, colNames = FALSE)

# put all data frames into list
al14df_list <- list(al14_dfA, al14_dfB, al14_dfC, al14_dfD)

# merge all data frames in list
al14D_df <- al14df_list %>% reduce(full_join, by = 'X1')

# Delete Duplicate Columns and rows (unsure where rows came from)
al14D_df <- al14D_df[-c(2,3,4), !duplicated(as.list(al14D_df))]

# # fill first row NA with blanks
# al14D_df2 <- al14D_df[1,]
#  al14D_df2[is.na(al14D_df2)] <- ""
# al14D_df[1,] <- al14D_df2[1,]
 
# merge first two rows for new column names
colnames(al14D_df) <- paste(sep = '.', as.character(unlist(al14D_df[1,])), as.character(unlist(al14D_df[2,])))
al14_df <- al14D_df[-c(1,2), ]

# Add Year
al14_df$Year <- 2014


```

#### 2015 

```{r}
# read data
al15_dfA <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2015 County Health Rankings Alabama Data - v3.xlsx", 
    sheet = 2,
    fillMergedCells = TRUE, colNames = FALSE)

al15_dfB <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2015 County Health Rankings Alabama Data - v3.xlsx", 
    sheet = 3,
    fillMergedCells = TRUE, colNames = FALSE)

al15_dfC <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2015 County Health Rankings Alabama Data - v3.xlsx", 
    sheet = 4,
    fillMergedCells = TRUE, colNames = FALSE)

al15_dfD <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2015 County Health Rankings Alabama Data - v3.xlsx", 
    sheet = 5,
    fillMergedCells = TRUE, colNames = FALSE)

# put all data frames into list
al15df_list <- list(al15_dfA, al15_dfB, al15_dfC, al15_dfD)

# merge all data frames in list
al15D_df <- al15df_list %>% reduce(full_join, by = 'X1')

# Delete Duplicate Columns and row (unsure where row came from)
al15D_df <- al15D_df[-c(2, 3, 4), !duplicated(as.list(al15D_df))]

# fill first row NA with blanks
al15D_df2 <- al15D_df[1,]
 al15D_df2[is.na(al15D_df2)] <- ""
al15D_df[1,] <- al15D_df2[1,]
 
# # merge first two rows for new column names
# colnames(al15D_df) <- paste(sep = '.', as.character(unlist(al15D_df[1,])), as.character(unlist(al15D_df[2,])))
# al15_df <- al15D_df[-c(1,2), ]

# Add Year
al15_df$Year <- 2015


```

#### 2016 

```{r}
# read data
al16_dfA <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2016 County Health Rankings Alabama Data - v3.xlsx", 
    sheet = 2,
    fillMergedCells = TRUE, colNames = FALSE)

al16_dfB <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2016 County Health Rankings Alabama Data - v3.xlsx", 
    sheet = 3,
    fillMergedCells = TRUE, colNames = FALSE)

al16_dfC <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2016 County Health Rankings Alabama Data - v3.xlsx", 
    sheet = 4,
    fillMergedCells = TRUE, colNames = FALSE)

al16_dfD <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2016 County Health Rankings Alabama Data - v3.xlsx", 
    sheet = 5,
    fillMergedCells = TRUE, colNames = FALSE)

# put all data frames into list
al16df_list <- list(al16_dfA, al16_dfB, al16_dfC, al16_dfD)

# merge all data frames in list
al16D_df <- al16df_list %>% reduce(full_join, by = 'X1')

# Delete Duplicate Columns and row (unsure where row came from)
al16D_df <- al16D_df[-c(2, 3, 4), !duplicated(as.list(al16D_df))]

# # fill first row NA with blanks
# al16D_df2 <- al16D_df[1,]
#  al16D_df2[is.na(al16D_df2)] <- ""
# al16D_df[1,] <- al16D_df2[1,]
#  
# merge first two rows for new column names
colnames(al16D_df) <- paste(sep = '.', as.character(unlist(al16D_df[1,])), as.character(unlist(al16D_df[2,])))
al16_df <- al16D_df[-c(1,2), ]

# Add Year
al16_df$Year <- 2016


```

#### 2017

```{r}
# read data
al17_dfA <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2017 County Health Rankings Alabama Data - v2.xlsx", 
    sheet = 2,
    fillMergedCells = TRUE, colNames = FALSE)

al17_dfB <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2017 County Health Rankings Alabama Data - v2.xlsx", 
    sheet = 3,
    fillMergedCells = TRUE, colNames = FALSE)

al17_dfC <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2017 County Health Rankings Alabama Data - v2.xlsx", 
    sheet = 4,
    fillMergedCells = TRUE, colNames = FALSE)

al17_dfD <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2017 County Health Rankings Alabama Data - v2.xlsx", 
    sheet = 5,
    fillMergedCells = TRUE, colNames = FALSE)

# put all data frames into list
al17df_list <- list(al17_dfA, al17_dfB, al17_dfC, al17_dfD)

# merge all data frames in list
al17D_df <- al17df_list %>% reduce(full_join, by = 'X1')

# Delete Duplicate Columns 
al17D_df <- al17D_df[!duplicated(as.list(al17D_df))]

# # fill first row NA with blanks
# al17D_df2 <- al17D_df[1,]
#  al17D_df2[is.na(al17D_df2)] <- ""
# al17D_df[1,] <- al17D_df2[1,]
 
# merge first two rows for new column names
colnames(al17D_df) <- paste(sep = '.', as.character(unlist(al17D_df[1,])), as.character(unlist(al17D_df[2,])))
al17_df <- al17D_df[-c(1,2), ]

# Add Year
al17_df$Year <- 2017


```

#### 2018 

```{r}
# read data
al18_dfA <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2018 County Health Rankings Alabama Data - v3.xlsx", 
    sheet = 2,
    fillMergedCells = TRUE, colNames = FALSE)

al18_dfB <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2018 County Health Rankings Alabama Data - v3.xlsx", 
    sheet = 3,
    fillMergedCells = TRUE, colNames = FALSE)

al18_dfC <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2018 County Health Rankings Alabama Data - v3.xlsx", 
    sheet = 4,
    fillMergedCells = TRUE, colNames = FALSE)

al18_dfD <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2018 County Health Rankings Alabama Data - v3.xlsx", 
    sheet = 5,
    fillMergedCells = TRUE, colNames = FALSE)

# put all data frames into list
al18df_list <- list(al18_dfA, al18_dfB, al18_dfC, al18_dfD)

# merge all data frames in list
al18D_df <- al18df_list %>% reduce(full_join, by = 'X1')

# Delete Duplicate Columns 
al18D_df <- al18D_df[!duplicated(as.list(al18D_df))]

# # fill first row NA with blanks
# al18D_df2 <- al18D_df[1,]
#  al18D_df2[is.na(al18D_df2)] <- ""
# al18D_df[1,] <- al18D_df2[1,]
 
# merge first two rows for new column names
colnames(al18D_df) <- paste(sep = '.', as.character(unlist(al18D_df[1,])), as.character(unlist(al18D_df[2,])))
al18_df <- al18D_df[-c(1,2), ]

# Add Year
al18_df$Year <- 2018


```

#### 2019 

```{r}
# read data
al19_dfA <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2019 County Health Rankings Alabama Data - v1_0.xlsx", 
    sheet = 2,
    fillMergedCells = TRUE, colNames = FALSE)

al19_dfB <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2019 County Health Rankings Alabama Data - v1_0.xlsx", 
    sheet = 3,
    fillMergedCells = TRUE, colNames = FALSE)

al19_dfC <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2019 County Health Rankings Alabama Data - v1_0.xlsx", 
    sheet = 4,
    fillMergedCells = TRUE, colNames = FALSE)

al19_dfD <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2019 County Health Rankings Alabama Data - v1_0.xlsx", 
    sheet = 5,
    fillMergedCells = TRUE, colNames = FALSE)

# put all data frames into list
al19df_list <- list(al19_dfA, al19_dfB, al19_dfC, al19_dfD)

# merge all data frames in list
al19D_df <- al19df_list %>% reduce(full_join, by = 'X1')

# Delete Duplicate Columns and row (unsure where row came from)
al19D_df <- al19D_df[ !duplicated(as.list(al19D_df))]

# # fill first row NA with blanks
# al19D_df2 <- al19D_df[1,]
#  al19D_df2[is.na(al19D_df2)] <- ""
# al19D_df[1,] <- al19D_df2[1,]
 
# merge first two rows for new column names
colnames(al19D_df) <- paste(sep = '.', as.character(unlist(al19D_df[1,])), as.character(unlist(al19D_df[2,])))
al19_df <- al19D_df[-c(1,2), ]

# Add Year
al19_df$Year <- 2019


```

#### Combine Alabama

```{r}
al_lst <- list(al11_df, al12_df, al13_df, al14_df, al15_df, al16_df, al17_df, al18_df, al19_df)

al_df <- rbindlist(al_lst, fill = TRUE)
```



## MISC TEST

```{r}
testdf<- X2011_County_Health_Ranking_Alabama_Data_v4 <- read.xlsx("Data Sets/Alabama Data/2011 County Health Ranking Alabama Data - v4.xlsx", 
    sheet = "Outcomes & Factors Rankings",
    fillMergedCells = TRUE, colNames = FALSE) 

df <- testdf[1,]
 df[is.na(df)] <- ""
testdf[1,] <- df[1,]
 
colnames(testdf) <- paste(sep = '.', as.character(unlist(testdf[1,])), as.character(unlist(testdf[2,])))
testdf <- testdf[-c(1,2), ]


```

```{r}
d <- X2011_County_Health_Ranking_Alabama_Data_v4 <- read_excel("Data Sets/Alabama Data/2011 County Health Ranking Alabama Data - v4.xls", 
    sheet = "Outcomes & Factors Rankings")
header <- colnames(d)
header <- header[!grepl("...", header)]

name_cols <- d[1,]
d <- d[-c(1,2),]
colnames(d) <- name_cols

header <- factor(rep(header, each = nrow(d) * (length(unique(colnames(d)))-1)),
                 levels = header)
header
```



library(readxl)
library(reshape)

# load an example excel file and see how it looks
d <- as.data.frame(read_excel("~/Bureau/Merged_Headers_Example.xls"))
d

##     X__1 January X__2 X__3 February X__4 X__5 March X__6 X__7
## 1 SECTOR    var1 var2 var3     var1 var2 var3  var1 var2 var3
## 2   AAAA       2    8    2        0    0    5     2    3    9
## 3   BBBB       9    3    8        4    2    6     8    6    8
## 4   CCCC       6    0   10        7    4    9     5    8    2
## 5   DDDD       0    1    2        2    5    7     4    3    2
## 6   EEEE       4    8    1        8   10    8     5   10    4
## 7   FFFF       1    0   10        2    1    4     1    3    3


# Capture the values of the merged cells on the first line
header <- colnames(d)
header <- header[!grepl("X__", header)]

# remove the first line and set the colomn names as the second line
name_cols <- d[1,]
d <- d[-1,]
colnames(d) <- name_cols

# Repeat the months the correct number of time 
# to be adapted depending on the structure of the file
# e.g. `-1` here is to not count the first column
header <- factor(rep(header, each = nrow(d) * (length(unique(colnames(d)))-1)),
                 levels = header)

```{r}
al11_dfA <- read.xlsx("Data Sets/Alabama Data/AnyConv.com__2011 County Health Ranking Alabama Data - v4.xlsx", 
    sheet = 2,
    fillMergedCells = TRUE, colNames = FALSE) %>%
  rename_with(.fn = \(cn) sapply(.[1.2,], \(c) paste(na.omit(c), collapse = "_"))) %>%
  slice(3:n())
```

