---
title: "Loop Data Upload"
author: "Julie Norman"
date: '2022-06-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library("tidyverse")
```

## States Data Upload

### Alabama

```{r}

al_files <- list.files("Data Sets/Alabama Data Source/Alabama xlsx/")

for(i in 1:length(al_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("al1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Alabama Data Source/Alabama xlsx/",
                   al_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
al13_dfF <- read.xlsx("Data Sets/Alabama Data Source/Alabama xlsx/AnyConv.com__2013 County Health Ranking Alabama Data - v1_1.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### Arkansas

```{r}

ak_files <- list.files("Data Sets/Arkansas Data Source/Arkansas xlsx/")

for(i in 1:length(ak_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("ak1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Arkansas Data Source/Arkansas xlsx/",
                   ak_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
ak13_dfF <- read.xlsx("Data Sets/Arkansas Data Source/Arkansas xlsx/AnyConv.com__2013 County Health Ranking Arkansas Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### Florida 

```{r}

fl_files <- list.files("Data Sets/Florida Data Source/Florida xlsx/")

for(i in 1:length(fl_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("fl1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Florida Data Source/Florida xlsx/",
                   fl_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
fl13_dfF <- read.xlsx("Data Sets/Florida Data Source/Florida xlsx/AnyConv.com__2013 County Health Ranking Florida Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)


```

### Georgia

```{r}

ga_files <- list.files("Data Sets/Georgia Data Source/Georgia xlsx/")

for(i in 1:length(ga_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("ga1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Georgia Data Source/Georgia xlsx/",
                   ga_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
ga13_dfF <- read.xlsx("Data Sets/Georgia Data Source/Georgia xlsx/AnyConv.com__2013 County Health Ranking Georgia Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### Illinois

```{r}

il_files <- list.files("Data Sets/Illinois Data Source/Illinois xlsx/")

for(i in 1:length(il_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("il1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Illinois Data Source/Illinois xlsx/",
                   il_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
il13_dfF <- read.xlsx("Data Sets/Illinois Data Source/Illinois xlsx/AnyConv.com__2013 County Health Ranking Illinois Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### Indiana

```{r}

in_files <- list.files("Data Sets/Indiana Data Source/Indiana xlsx/")

for(i in 1:length(in_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("in1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Indiana Data Source/Indiana xlsx/",
                   in_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
in13_dfF <- read.xlsx("Data Sets/Indiana Data Source/Indiana xlsx/AnyConv.com__2013 County Health Ranking Indiana Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### Iowa

```{r}

ia_files <- list.files("Data Sets/Iowa Data Source/Iowa xlsx/")

for(i in 1:length(ia_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("ia1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Iowa Data Source/Iowa xlsx/",
                   ia_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
ia13_dfF <- read.xlsx("Data Sets/Iowa Data Source/Iowa xlsx/AnyConv.com__2013 County Health Ranking Iowa Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### Kansas

```{r}

ks_files <- list.files("Data Sets/Kansas Data Source/Kansas xlsx/")

for(i in 1:length(ks_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("ks1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Kansas Data Source/Kansas xlsx/",
                   ks_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
ks13_dfF <- read.xlsx("Data Sets/Kansas Data Source/Kansas xlsx/AnyConv.com__2013 County Health Ranking Kansas Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### Kentucky

```{r}

ky_files <- list.files("Data Sets/Kentucky Data Source/Kentucky xlsx/")

for(i in 1:length(ky_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("ky1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Kentucky Data Source/Kentucky xlsx/",
                   ky_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
ky13_dfF <- read.xlsx("Data Sets/Kentucky Data Source/Kentucky xlsx/AnyConv.com__2013 County Health Ranking Kentucky Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### Louisiana 

```{r}

la_files <- list.files("Data Sets/Louisiana Data Source/Louisiana xlsx/")

for(i in 1:length(la_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("la1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Louisiana Data Source/Louisiana xlsx/",
                   la_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
la13_dfF <- read.xlsx("Data Sets/Louisiana Data Source/Louisiana xlsx/AnyConv.com__2013 County Health Ranking Louisiana Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### Minnesota

```{r}

mn_files <- list.files("Data Sets/Minnesota Data Source/Minnesota xlsx/")

for(i in 1:length(mn_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("mn1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Minnesota Data Source/Minnesota xlsx/",
                   mn_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
mn13_dfF <- read.xlsx("Data Sets/Minnesota Data Source/Minnesota xlsx/AnyConv.com__2013 County Health Ranking Minnesota Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)


```

### Mississippi

```{r}

ms_files <- list.files("Data Sets/Mississippi Data Source/Mississippi xlsx/")

for(i in 1:length(ms_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("ms1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Mississippi Data Source/Mississippi xlsx/",
                   ms_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
ms13_dfF <- read.xlsx("Data Sets/Mississippi Data Source/Mississippi xlsx/AnyConv.com__2013 County Health Ranking Mississippi Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### Missouri cleaned

```{r}

mo_files <- list.files("Data Sets/Missouri Data Source/Missouri xlsx/")

for(i in 1:length(mo_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("mo1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Missouri Data Source/Missouri xlsx/",
                   mo_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
mo13_dfF <- read.xlsx("Data Sets/Missouri Data Source/Missouri xlsx/AnyConv.com__2013 County Health Ranking Missouri Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### Montana

```{r}

mt_files <- list.files("Data Sets/Montana Data Source/Montana xlsx/")

for(i in 1:length(mt_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("mt1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Montana Data Source/Montana xlsx/",
                   mt_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
mt13_dfF <- read.xlsx("Data Sets/Montana Data Source/Montana xlsx/AnyConv.com__2013 County Health Ranking Montana Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### Nebraska

```{r}

ne_files <- list.files("Data Sets/Nebraska Data Source/Nebraska xlsx/")

for(i in 1:length(ne_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("ne1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Nebraska Data Source/Nebraska xlsx/",
                   ne_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
ne13_dfF <- read.xlsx("Data Sets/Nebraska Data Source/Nebraska xlsx/AnyConv.com__2013 County Health Ranking Nebraska Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### North Carolina

```{r}
# Data upload 

nc_files <- list.files("Data Sets/North Carolina Data Source/North Carolina xlsx/")

for(i in 1:length(nc_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("nc1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/North Carolina Data Source/North Carolina xlsx/",
                   nc_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
nc13_dfF <- read.xlsx("Data Sets/North Carolina Data Source/North Carolina xlsx/AnyConv.com__2013 County Health Ranking North Carolina Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### North Dakota

```{r}
# Data upload 

nd_files <- list.files("Data Sets/North Dakota Data Source/North Dakota xlsx/")

for(i in 1:length(nd_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("nd1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/North Dakota Data Source/North Dakota xlsx/",
                   nd_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
nd13_dfF <- read.xlsx("Data Sets/North Dakota Data Source/North Dakota xlsx/AnyConv.com__2013 County Health Ranking North Dakota Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### South Carolina

```{r}
# Data upload 

sc_files <- list.files("Data Sets/South Carolina Data Source/South Carolina xlsx/")

for(i in 1:length(sc_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("sc1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/South Carolina Data Source/South Carolina xlsx/",
                   sc_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
sc13_dfF <- read.xlsx("Data Sets/South Carolina Data Source/South Carolina xlsx/AnyConv.com__2013 County Health Ranking South Carolina Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### South Dakota

```{r}
# Data upload 

sd_files <- list.files("Data Sets/South Dakota Data Source/South Dakota xlsx/")

for(i in 1:length(sc_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("sd1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/South Dakota Data Source/South Dakota xlsx/",
                   sd_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
sd13_dfF <- read.xlsx("Data Sets/South Dakota Data Source/South Dakota xlsx/AnyConv.com__2013 County Health Ranking South Dakota Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### Tennessee

```{r}
# Data upload 

tn_files <- list.files("Data Sets/Tennessee Data Source/Tennessee xlsx/")

for(i in 1:length(tn_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("tn1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Tennessee Data Source/Tennessee xlsx/",
                   tn_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
tn13_dfF <- read.xlsx("Data Sets/Tennessee Data Source/Tennessee xlsx/AnyConv.com__2013 County Health Ranking Tennessee Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### Virginia

```{r}

va_files <- list.files("Data Sets/Virginia Data Source/Virginia xlsx/")

for(i in 1:length(va_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("va1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Virginia Data Source/Virginia xlsx/",
                   va_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
va13_dfF <- read.xlsx("Data Sets/Virginia Data Source/Virginia xlsx/AnyConv.com__2013 County Health Ranking Virginia Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### West Virginia

```{r}
# Data upload 

wv_files <- list.files("Data Sets/West Virginia Data Source/West Virginia xlsx/")

for(i in 1:length(wv_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("wv1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/West Virginia Data Source/West Virginia xlsx/",
                   wv_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
wv13_dfF <- read.xlsx("Data Sets/West Virginia Data Source/West Virginia xlsx/AnyConv.com__2013 County Health Ranking West Virginia Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### Wisconsin

```{r}
# Data upload 

wi_files <- list.files("Data Sets/Wisconsin Data Source/Wisconsin xlsx/")

for(i in 1:length(wi_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("wi1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Wisconsin Data Source/Wisconsin xlsx/",
                   wi_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
wi13_dfF <- read.xlsx("Data Sets/Wisconsin Data Source/Wisconsin xlsx/AnyConv.com__2013 County Health Ranking Wisconsin Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```

### Wyoming

```{r}
# Data upload 

wy_files <- list.files("Data Sets/Wyoming Data Source/Wyoming xlsx/")

for(i in 1:length(wy_files)) { 
  for (j in 2:5) {
    
  # Head of for-loop
  assign(paste0("wy1", i, "_df", LETTERS[j]),                                   
  # Read and store data frames
         read.xlsx(paste0("Data Sets/Wyoming Data Source/Wyoming xlsx/",
                   wy_files[i]), 
                   sheet = (j),
                   fillMergedCells = TRUE, 
                   colNames = FALSE))
    
  }
}

# Extra sheet in year 2013
wy13_dfF <- read.xlsx("Data Sets/Wyoming Data Source/Wyoming xlsx/AnyConv.com__2013 County Health Ranking Wyoming Data - v1_0.xlsx", 
    sheet = 6,
    fillMergedCells = TRUE, colNames = FALSE)

```




## Combine Data by Year

```{r}
state <- c("al", "ak", "fl", "ga", "il", "in", "ia", "ks", "ky", "la", "mn", "ms", "mo", "mt", "ne", "nc", "nd", "sc", "sd", "tn", "va", "wv", "wi", "wy")
```


### 2011

```{r}

datalist11 = list()

for(i in state){

# put all data frames into list
assign(paste0(i, "11df_list"),
       list(get(paste0(i, "11_dfB")), 
            get(paste0(i, "11_dfC")), 
            get(paste0(i, "11_dfD")), 
            get(paste0(i, "11_dfE"))))
    
# merge all data frames in list
assign(paste0(i, "11D_df"),
       (get(paste0(i, "11df_list")) %>% 
          reduce(full_join, by = 'X1')
        ))

# Delete Duplicate Columns and row (unsure where row came from)
assign(paste0(i, "11D_df2"), get(paste0(i, "11D_df")) %>%
         slice(-2) %>%
         select(-which(duplicated(as.list(get(paste0(i, "11D_df"))))))
         )

# merge first two rows for new column names
 assign(paste0(i, "11D_newnames"), paste(
             slice(get(paste0(i, "11D_df2")), 1),
             slice(get(paste0(i, "11D_df2")), 2),
             sep = '.'))
 
 # delete old column rows
assign(paste0(i, "11D_df3"), get(paste0(i, "11D_df2")) %>%
         slice(-c(1, 2))) 
 
# add new column names
assign(paste0(i, "11_df"), 
       setnames(get(paste0(i, "11D_df3")), 
                colnames(get(paste0(i, "11D_df2"))), 
                get(paste0(i, "11D_newnames"))))

# Add Year
Year <- 2011
assign(paste0(i, "11_df"), cbind(get(paste0(i, "11_df")), Year))


# List of Datasets
datalist11[[i]] <- get(paste0(i, "11_df"))


}

# Combine Datasets
all_df11 <- do.call(rbind, datalist11)

# lowercase column names
names(all_df11) <- tolower(names(all_df11))

# Find Unique Column Names
unique_names <- unique(colnames(all_df11))

# Keep Only Unique Column Names
all_df11 <- all_df11[unique_names]


```

### 2012

```{r}

datalist12 = list()

for(i in state){

# put all data frames into list
assign(paste0(i, "12df_list"),
       list(get(paste0(i, "12_dfB")), 
            get(paste0(i, "12_dfC")), 
            get(paste0(i, "12_dfD")), 
            get(paste0(i, "12_dfE"))))
    
# merge all data frames in list
assign(paste0(i, "12D_df"),
       (get(paste0(i, "12df_list")) %>% 
          reduce(full_join, by = 'X1')
        ))

# Delete Duplicate Columns and row (unsure where row came from)
assign(paste0(i, "12D_df2"), get(paste0(i, "12D_df")) %>%
         select(-which(duplicated(as.list(get(paste0(i, "12D_df"))))))
         )

# merge first two rows for new column names
 assign(paste0(i, "12D_newnames"), paste(
             slice(get(paste0(i, "12D_df2")), 1),
             slice(get(paste0(i, "12D_df2")), 2),
             sep = '.'))
 
 # delete old column rows
assign(paste0(i, "12D_df3"), get(paste0(i, "12D_df2")) %>%
         slice(-c(1, 2))) 
 
# add new column names
assign(paste0(i, "12_df"), 
       setnames(get(paste0(i, "12D_df3")), 
                colnames(get(paste0(i, "12D_df2"))), 
                get(paste0(i, "12D_newnames"))))

# Add Year
Year <- 2012
assign(paste0(i, "12_df"), cbind(get(paste0(i, "12_df")), Year))


# List of Datasets
datalist12[[i]] <- get(paste0(i, "12_df"))


}

# Combine Datasets
all_df12 <- do.call(rbind, datalist12)

# lowercase column names
names(all_df12) <- tolower(names(all_df12))

# Find Unique Column Names
unique_names <- unique(colnames(all_df12))

# Keep Only Unique Column Names
all_df12 <- all_df12[unique_names]


```

### 2013 *Need to delete cell in files

```{r}

datalist13 = list()

for(i in state){

# put all data frames into list
assign(paste0(i, "13df_list"),
       list(get(paste0(i, "13_dfB")), 
            get(paste0(i, "13_dfC")), 
            get(paste0(i, "13_dfD")), 
            get(paste0(i, "13_dfE")), 
            get(paste0(i, "13_dfF"))))
    
# merge all data frames in list
assign(paste0(i, "13D_df"),
       (get(paste0(i, "13df_list")) %>% 
          reduce(full_join, by = 'X1')
        ))

# Delete Duplicate Columns and row (unsure where row came from)
assign(paste0(i, "13D_df2"), get(paste0(i, "13D_df")) %>%
         select(-which(duplicated(as.list(get(paste0(i, "13D_df"))))))
         )

# merge first two rows for new column names
 assign(paste0(i, "13D_newnames"), paste(
             slice(get(paste0(i, "13D_df2")), 1),
             slice(get(paste0(i, "13D_df2")), 2),
             sep = '.'))
 
 # delete old column rows
assign(paste0(i, "13D_df3"), get(paste0(i, "13D_df2")) %>%
         slice(-c(1, 2))) 
 
# add new column names
assign(paste0(i, "13_df"), 
       setnames(get(paste0(i, "13D_df3")), 
                colnames(get(paste0(i, "13D_df2"))), 
                get(paste0(i, "13D_newnames"))))

# Add Year
Year <- 2013
assign(paste0(i, "13_df"), cbind(get(paste0(i, "13_df")), Year))


# List of Datasets
datalist13[[i]] <- get(paste0(i, "13_df"))


}

# Combine Datasets
all_df13 <- do.call(bind_rows, datalist13)

# lowercase column names
names(all_df13) <- tolower(names(all_df13))

# Find Unique Column Names
unique_names <- unique(colnames(all_df13))

# Keep Only Unique Column Names
all_df13 <- all_df13[unique_names]



```

```{r}
state <- c("al", "ak", "fl", "ga", "il", "in", "ia", "ks", "ky", "la", "mn", "ms", "mo", "mt", "ne", "nc", "nd", "sc", "sd", "tn", "va", "wv", "wi", "wy")

state <- c("al", "ak", "fl", "ga", "il", "in", "ia", "ks", "ky", "la", "mn", "ms", "mo", "mt", "ne", "nc", "nd", "sc", "sd", "tn", "va", "wv", "wi", "wy")

#setdiff(colnames(al17_df), colnames(mo17_df))
```


### 2014 

```{r}

datalist14 = list()

for(i in state){

# put all data frames into list
assign(paste0(i, "14df_list"),
       list(get(paste0(i, "14_dfB")), 
            get(paste0(i, "14_dfC")), 
            get(paste0(i, "14_dfD")), 
            get(paste0(i, "14_dfE"))))
    
# merge all data frames in list
assign(paste0(i, "14D_df"),
       (get(paste0(i, "14df_list")) %>% 
          reduce(full_join, by = 'X1')
        ))

# Delete Duplicate Columns and row (unsure where row came from)
assign(paste0(i, "14D_df2"), get(paste0(i, "14D_df")) %>%
         select(-which(duplicated(as.list(get(paste0(i, "14D_df"))))))
         )

# merge first two rows for new column names


 assign(paste0(i, "14D_newnames"), paste(
             slice(get(paste0(i, "14D_df2")), 1),
             slice(get(paste0(i, "14D_df2")), 5),
             sep = '.'))
 
 # delete old column rows
assign(paste0(i, "14D_df3"), get(paste0(i, "14D_df2")) %>%
         slice(-c(1, 2, 3, 4, 5))) 
 
# add new column names
assign(paste0(i, "14_df"), 
       setnames(get(paste0(i, "14D_df3")), 
                colnames(get(paste0(i, "14D_df2"))), 
                get(paste0(i, "14D_newnames"))))

# Add Year
Year <- 2014
assign(paste0(i, "14_df"), cbind(get(paste0(i, "14_df")), Year))


# List of Datasets
datalist14[[i]] <- get(paste0(i, "14_df"))


}

# Combine Datasets
all_df14 <- do.call(rbind, datalist14)

# lowercase column names
names(all_df14) <- tolower(names(all_df14))

# Find Unique Column Names
unique_names <- unique(colnames(all_df14))

# Keep Only Unique Column Names
all_df14 <- all_df14[unique_names]

#setdiff(colnames(al14_df), colnames(ak14_df))
```

### 2015

```{r}

datalist15 = list()

for(i in state){

# put all data frames into list
assign(paste0(i, "15df_list"),
       list(get(paste0(i, "15_dfB")), 
            get(paste0(i, "15_dfC")), 
            get(paste0(i, "15_dfD")), 
            get(paste0(i, "15_dfE"))))
    
# merge all data frames in list
assign(paste0(i, "15D_df"),
       (get(paste0(i, "15df_list")) %>% 
          reduce(full_join, by = 'X1')
        ))

# Delete Duplicate Columns and row (unsure where row came from)
assign(paste0(i, "15D_df2"), get(paste0(i, "15D_df")) %>%
         slice(-c(2, 3, 4)) %>%
         select(-which(duplicated(as.list(get(paste0(i, "15D_df"))))))
         )

# merge first two rows for new column names
 assign(paste0(i, "15D_newnames"), paste(
             slice(get(paste0(i, "15D_df2")), 1),
             slice(get(paste0(i, "15D_df2")), 2),
             sep = '.'))
 
 # delete old column rows
assign(paste0(i, "15D_df3"), get(paste0(i, "15D_df2")) %>%
         slice(-c(1, 2))) 
 
# add new column names
assign(paste0(i, "15_df"), 
       setnames(get(paste0(i, "15D_df3")), 
                colnames(get(paste0(i, "15D_df2"))), 
                get(paste0(i, "15D_newnames"))))

# Add Year
Year <- 2015
assign(paste0(i, "15_df"), cbind(get(paste0(i, "15_df")), Year))


# List of Datasets
datalist15[[i]] <- get(paste0(i, "15_df"))


}

# Combine Datasets
all_df15 <- do.call(rbind, datalist15)

# lowercase column names
names(all_df15) <- tolower(names(all_df15))

# Find Unique Column Names
unique_names <- unique(colnames(all_df15))

# Keep Only Unique Column Names
all_df15 <- all_df15[unique_names]

```


### 2016

```{r}

datalist16 = list()

for(i in state){

# put all data frames into list
assign(paste0(i, "16df_list"),
       list(get(paste0(i, "16_dfB")), 
            get(paste0(i, "16_dfC")), 
            get(paste0(i, "16_dfD")), 
            get(paste0(i, "16_dfE"))))
    
# merge all data frames in list
assign(paste0(i, "16D_df"),
       (get(paste0(i, "16df_list")) %>% 
          reduce(full_join, by = 'X1')
        ))

# Delete Duplicate Columns and row (unsure where row came from)
assign(paste0(i, "16D_df2"), get(paste0(i, "16D_df")) %>%
         slice(-c(2, 3, 4)) %>%
         select(-which(duplicated(as.list(get(paste0(i, "16D_df"))))))
         )

# merge first two rows for new column names
 assign(paste0(i, "16D_newnames"), paste(
             slice(get(paste0(i, "16D_df2")), 1),
             slice(get(paste0(i, "16D_df2")), 2),
             sep = '.'))
 
 # delete old column rows
assign(paste0(i, "16D_df3"), get(paste0(i, "16D_df2")) %>%
         slice(-c(1, 2))) 
 
# add new column names
assign(paste0(i, "16_df"), 
       setnames(get(paste0(i, "16D_df3")), 
                colnames(get(paste0(i, "16D_df2"))), 
                get(paste0(i, "16D_newnames"))))

# Add Year
Year <- 2016
assign(paste0(i, "16_df"), cbind(get(paste0(i, "16_df")), Year))

# List of Datasets
datalist16[[i]] <- get(paste0(i, "16_df"))


}

# Combine Datasets
all_df16 <- do.call(bind_rows, datalist16)

# lowercase column names
names(all_df16) <- tolower(names(all_df16))

# Find Unique Column Names
unique_names <- unique(colnames(all_df16))

# Keep Only Unique Column Names
all_df16 <- all_df16[unique_names]

#setdiff(colnames(al16_df), colnames(ak16_df))
```

### 2017

```{r}

datalist17 = list()

for(i in state){

# put all data frames into list
assign(paste0(i, "17df_list"),
       list(get(paste0(i, "17_dfB")), 
            get(paste0(i, "17_dfC")), 
            get(paste0(i, "17_dfD")), 
            get(paste0(i, "17_dfE"))))
    
# merge all data frames in list
assign(paste0(i, "17D_df"),
       (get(paste0(i, "17df_list")) %>% 
          reduce(full_join, by = 'X1')
        ))

# Delete Duplicate Columns and row (unsure where row came from)
assign(paste0(i, "17D_df2"), get(paste0(i, "17D_df")) %>%
         select(-which(duplicated(as.list(get(paste0(i, "17D_df"))))))
         )

# merge first two rows for new column names
 assign(paste0(i, "17D_newnames"), paste(
             slice(get(paste0(i, "17D_df2")), 1),
             slice(get(paste0(i, "17D_df2")), 2),
             sep = '.'))
 
 # delete old column rows
assign(paste0(i, "17D_df3"), get(paste0(i, "17D_df2")) %>%
         slice(-c(1, 2))) 
 
# add new column names
assign(paste0(i, "17_df"), 
       setnames(get(paste0(i, "17D_df3")), 
                colnames(get(paste0(i, "17D_df2"))), 
                get(paste0(i, "17D_newnames"))))

# Add Year
Year <- 2017
assign(paste0(i, "17_df"), cbind(get(paste0(i, "17_df")), Year))

# List of Datasets
datalist17[[i]] <- get(paste0(i, "17_df"))


}

# Combine Datasets
all_df17 <- do.call(bind_rows, datalist17)

# Drop redundant columns
all_df17 <- subset(all_df17, select = -c(NA.County...20, NA.County...3))

# lowercase column names
names(all_df17) <- tolower(names(all_df17))

# Find Unique Column Names
unique_names <- unique(colnames(all_df17))

# Keep Only Unique Column Names
all_df17 <- all_df17[unique_names]

```

### 2018

```{r}

datalist18 = list()

for(i in state){

# put all data frames into list
assign(paste0(i, "18df_list"),
       list(get(paste0(i, "18_dfB")), 
            get(paste0(i, "18_dfC")), 
            get(paste0(i, "18_dfD")), 
            get(paste0(i, "18_dfE"))))
    
# merge all data frames in list
assign(paste0(i, "18D_df"),
       (get(paste0(i, "18df_list")) %>% 
          reduce(full_join, by = 'X1')
        ))

# Delete Duplicate Columns and row (unsure where row came from)
assign(paste0(i, "18D_df2"), get(paste0(i, "18D_df")) %>%
         select(-which(duplicated(as.list(get(paste0(i, "18D_df"))))))
         )

# merge first two rows for new column names
 assign(paste0(i, "18D_newnames"), paste(
             slice(get(paste0(i, "18D_df2")), 1),
             slice(get(paste0(i, "18D_df2")), 2),
             sep = '.'))
 
 # delete old column rows
assign(paste0(i, "18D_df3"), get(paste0(i, "18D_df2")) %>%
         slice(-c(1, 2))) 
 
# add new column names
assign(paste0(i, "18_df"), 
       setnames(get(paste0(i, "18D_df3")), 
                colnames(get(paste0(i, "18D_df2"))), 
                get(paste0(i, "18D_newnames"))))

# Add Year
Year <- 2018
assign(paste0(i, "18_df"), cbind(get(paste0(i, "18_df")), Year))

# List of Datasets
datalist18[[i]] <- get(paste0(i, "18_df"))


}

# Combine Datasets
all_df18 <- do.call(rbind, datalist18)

# lowercase column names
names(all_df18) <- tolower(names(all_df18))

# Find Unique Column Names
unique_names <- unique(colnames(all_df18))

# Keep Only Unique Column Names
all_df18 <- all_df18[unique_names]

```

### 2019

```{r}

datalist19 = list()

for(i in state){

# put all data frames into list
assign(paste0(i, "19df_list"),
       list(get(paste0(i, "19_dfB")), 
            get(paste0(i, "19_dfC")), 
            get(paste0(i, "19_dfD")), 
            get(paste0(i, "19_dfE"))))
    
# merge all data frames in list
assign(paste0(i, "19D_df"),
       (get(paste0(i, "19df_list")) %>% 
          reduce(full_join, by = 'X1')
        ))

# Delete Duplicate Columns and row (unsure where row came from)
assign(paste0(i, "19D_df2"), get(paste0(i, "19D_df")) %>%
         select(-which(duplicated(as.list(get(paste0(i, "19D_df"))))))
         )

# merge first two rows for new column names
 assign(paste0(i, "19D_newnames"), paste(
             slice(get(paste0(i, "19D_df2")), 1),
             slice(get(paste0(i, "19D_df2")), 2),
             sep = '.'))
 
 # delete old column rows
assign(paste0(i, "19D_df3"), get(paste0(i, "19D_df2")) %>%
        slice(-c(1, 2))) 
 
# add new column names
assign(paste0(i, "19_df"), 
       setnames(get(paste0(i, "19D_df3")), 
                colnames(get(paste0(i, "19D_df2"))), 
                get(paste0(i, "19D_newnames"))))

# Add Year
Year <- 2019
assign(paste0(i, "19_df"), cbind(get(paste0(i, "19_df")), Year))

# List of Datasets
datalist19[[i]] <- get(paste0(i, "19_df"))


}

# Combine Datasets
all_df19 <- do.call(rbind, datalist19)

# lowercase column names
names(all_df19) <- tolower(names(all_df19))

# Find Unique Column Names
unique_names <- unique(colnames(all_df19))

# Keep Only Unique Column Names
all_df19 <- all_df19[unique_names]


```

## Combine all data years

```{r}
datalist <- list()

for(i in 1:9){
  
  # list of yearly dataframes
  datalist[[i]] <- get(paste0("all_df1", i))
  
}
# Combine Datasets
all_df <- do.call(bind_rows, datalist)
```

## Additional Data Cleaning

```{r}

# Delete extra columns 
all_df2 <- all_df %>% 
  relocate(year, .before = 'health outcomes.z-score') %>%
  rename(county = na.county, state = na.state, fips = na.fips) %>%
  subset (select = -c( `access to healthy foods.# zip codes...150`,
                       `access to healthy foods.# zip codes...204`,
                       `access to healthy foods.% healthy foods...151`,
                       `access to healthy foods.% healthy foods...205`,
                       `access to healthy foods.zip codes with healthy foods...149`,
                       `access to healthy foods.zip codes with healthy foods...203`, 
                       `children in poverty.% children in poverty - black`,
                       `children in poverty.% children in poverty (black)`,
                       `children in poverty.% children in poverty - hispanic`,
                       `children in poverty.% children in poverty (hispanic)`,
                       `children in poverty.% children in poverty - white`,
                       `children in poverty.% children in poverty (white)`,
                       `driving alone to work.% drive alone (black)`,
                       `driving alone to work.% drive alone - black`,
                       `driving alone to work.% drive alone (hispanic)`,
                       `driving alone to work.% drive alone - hispanic`,
                       `driving alone to work.% drive alone (white)`,
                       `driving alone to work.% drive alone - white`
                       )) %>% 
  mutate(`severe housing problems.# household` = 
           coalesce(all_df$`severe housing problems.# household with severe problems`, 
            all_df$`severe housing problems.# households with severe problems` )) %>% 
  mutate(`demographics.# american indian/ native alaskan` = 
           coalesce(all_df$`demographics.# american indian/ alaskan native`, 
            all_df$`demographics.# american indian/alaskan native` )) %>% 
  mutate(`demographics.# native hawaiian/ pacific islander` = 
           coalesce(all_df$`demographics.# native hawaiian/ other pacific islander`, 
            all_df$`demographics.# native hawaiian/other pacific islander` )) %>% 
  mutate(`demographics.% american indian/ native alaskan` = 
           coalesce(all_df$`demographics.% american indian/ alaskan native`, 
            all_df$`demographics.% american indian/alaskan native` )) %>% 
  mutate(`demographics.% native hawaiian/ pacific islander` = 
           coalesce(all_df$`demographics.% native hawaiian/ other pacific islander`, 
            all_df$`demographics.% native hawaiian/other pacific islander` )) %>% 
  mutate(demographics.populationA = 
           coalesce(all_df$`demographics.population`, 
            all_df$`demographics.population...164` )) 


```


```{r}


test_df <- all_df %>% select(na.state, na.county, year, demographics.population, demographics.population...147, demographics.population...156, demographics.population...155, demographics.population...164 )

# Delete Columns 
# NA.NA...1, NA.NA...2, NA.NA...3

# all_df$`Access to healthy foods.% Healthy Foods...205`

sum(is.na(all_df2$demographics.population...147))

all_df2$demographics.populationA

```

 

```{r}
colnames(all_df2[ , order(names(all_df2))])
```

Demographics.Population: 6154
Demographics.Population...164: 16405
Demographics.Population...155: 16405
Demographics.Population...156: 16405

`Access to healthy foods.# Zip Codes`: 16410
`Access to healthy foods.Zip Codes with Healthy Foods...149`: all na
`Access to healthy foods.# Zip Codes...150`: all na

`Access to healthy foods.% Healthy Food`: 16410
`Access to healthy foods.% Healthy Foods...151`: all na
`Access to healthy foods.% Healthy Foods...205`: 16410

